---
title: "AGILE PhD School 2022"
description: |
  Welcome to the website. I hope you enjoy it!
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```


```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "GeoTecINIT/agilephdschool2022") %>%
  meta_social(
    title = "AGILE PhD School 2022",
    url ="https://geotecinit.github.io/agilephdschool2022/"
  )
```


**6th AGILE PhD School 2022** - *Make your work more open and reproducible*

June 1st – 3rd 2022, [Institute of New Imaging Technologies](https://www.init.uji.es/?lang=en), Universitat Jaume I, Castellón (Spain)

The AGILE PhD school aims to bring PhD students from different countries together. The purpose of the school is to offer a platform for PhD students to present their research to date, exchange ideas, learn and discuss geospatial methods and acquire and improve skills related to geoinformatics. This will allow participants to:  

-   be exposed to the diversity of fields and common features of our domain  
-   exchange ideas about the PhD process itself  
-   develop their own network
-   be exposed to the reproducibility and reproducibility practices in Geoscience and GIScience.

## Programme

### Day 1 (31 May 2022, Tuesday) 

Arrival of participants to [Doña Lola hotel](http://www.hoteldonalola.com/)

### Day 2 (1 June 2022, Wednesday)

**Facilitators**: Vicent Beltrán Palanques, Carlos Granell

**Meeting room**: Espaitec2, [UB1206SM](http://smart.uji.es/index.php?room=UB1206SM), 2nd floor.

**Morning session** 

9:00 - 10:00 Welcome and logistics (Carlos)

Coffee break

10:30 - 13:30 Topic: Three-minute thesis presentations (3MTP)  

-	Academic spoken genres and multimodality 

-	Three-Minute Thesis Presentations: The genre, characteristics, and structure. 

-	Preparation of Three-Minute Thesis Presentations 

**13:30 - 15:00, Lunch break** at *Restaurante Agora* in campus   

**Afternoon session**

15:00 - 17:00 Participants' presentations and discussion (2 hours)

**Dinner** at TBC 


### Day 3 (2 June 2022, Thursday)

**Facilitators**: [Frank Ostermann](https://research.utwente.nl/en/persons/frank-ostermann), Carlos Granell

**Meeting room**: School of Sciences, [TD0112FR](http://smart.uji.es/index.php?room=TD0112FR), 1st floor. 


**Morning session** 

Topic: what are reproducibility/replicability and how to ensure it


**13:30 - 15:00, Lunch break** at *Restaurante Agora* in campus   

**Afternoon session** 

-   reproducible plan exercise

-   peer assessment

**Dinner** at TBC 

### Day 4 (3 June 2022, Friday)

**Facilitators**: [Frank Ostermann](https://research.utwente.nl/en/persons/frank-ostermann), Carlos Granell

**Meeting room**: Espaitec2, [UB1206SM](http://smart.uji.es/index.php?room=UB1206SM), 2nd floor.

**Morning session** 

-   Group discussion: what open science means for their work, what concerns they have, barriers to openness like feeling unsure about the quality of their work/code, 

-   Presentations: take-away message of each participant (reproducible plan, etc)

-   Closing remarks

**13:30 - 15:00, Lunch break** at *Restaurante Agora* in campus   
